30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex

@@

>>>>

		As we saw, the directory service generates overhead of the network. If we could replace this central authority, we could reduce the overhead of the network and improve the performance. This means, we would like to have Tor decentralized. Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up. This is due to the fact that there are many problems decentralization brings along with.

@@

		\subsection{Key exchange}
		When using a decentralized network, using a centralized authority for managing the keys, is not possible. This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them. Diffie-Hellman is a very popular algorithm for exchanging keys between two parties. Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties. This makes it possible for the adversary to decrypt all message sent between the two parties.

		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace]. This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit. There are several proposals for more efficient key exchange methods. One of them is ACE, an one-way authenticated key exchange protocol. The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers. ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
